### 2022-09-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@874f7288455de1541869d033d96cf77a2bb42ac3 🚀

        {\bfseries 1.:}\,Community ecologists are increasingly shifting
from a binary thinking of ecological networks (e.g., do species
interact?) to a more probabilistic perspective (e.g., how likely are
species to interact?). Assuredly, the benefits of representing
ecological interactions as probabilistic events are numerous, from a
better assessment of the spatial variation of interactions to an
increase capacity to reconstruct networks from sparse data.\\%
        {\bfseries 2.:}\,However, probabilities need to be used with
caution when working with ecological networks. Indeed, depending on the
system at hand and the method used to built probabilistic networks,
probabilities can have different interpretations that imply different
ways to manipulate them. This is rarely discussed in the literature,
thus impeding our ability to use data on probabilistic interactions
appropriately.\\%
        {\bfseries 3.:}\,At the core of these differences lie the
distinction between assessing if two groups of individuals \emph{can}
interact or if they \emph{will} interact. This impacts the spatial,
temporal, and taxonomic scaling of interaction probabilities, thus
enlightening the need to properly define them in their ecological
context.\\%
        {\bfseries 4.:}\,With these challenges in mind, we call for a
better definition and conceptualization of probabilistic ecological
networks, both at the local and regional scales, and propose a general
approach to thinking about probabilities in regards to ecological
interactions.\\%

>>>>

        {\bfseries 1:}\,Community ecologists are increasingly shifting
from a binary thinking of ecological networks (e.g., do species
interact?) to a more probabilistic perspective (e.g., how likely are
species to interact?). Assuredly, the benefits of representing
ecological interactions as probabilistic events are numerous, from a
better assessment of the spatial variation of interactions to an
increase capacity to reconstruct networks from sparse data.\\%
        {\bfseries 2:}\,However, probabilities need to be used with
caution when working with ecological networks. Indeed, depending on the
system at hand and the method used to build probabilistic networks,
probabilities can have different interpretations that imply different
ways to manipulate them. This is rarely discussed in the literature,
thus impeding our ability to use data on probabilistic interactions
appropriately.\\%
        {\bfseries 3:}\,At the core of these differences lie the
distinction between assessing the likelihood that two groups of
individuals \emph{can} interact and the likelihood that they \emph{will}
interact. This impacts the spatial, temporal, and taxonomic scaling of
interaction probabilities, thus further enlightening the need to
properly define them in their ecological context.\\%
        {\bfseries 4:}\,With these challenges in mind, we propose a
general approach to thinking about probabilities in regards to
ecological interactions, and call for better definitions and
conceptualizations of probabilistic ecological networks, both at the
local and regional scales.\\%
